---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Luckiest+Guy&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Didact+Gothic&family=Luckiest+Guy&display=swap');
h1 {
  font-family: 'Luckiest Guy';
  background-color: #BCECAC;
  padding: 10px 10px;
  display: inline-block;
}
h2 {
  background-color: #BCECAC;
  font-family: 'Didact Gothic';
  padding: 5px 1px;
  display: inline-block;
}
body {
  font-family: 'Didact Gothic';
  font-size: 20px;
}
```

## What are the body language tendencies for different ages and genders?

Positive Gestural Hemispheric Tendency (PGHT) is the side a person will tend to use when experience positive feelings or emotions. For example, if a person's PGHT is right, they will tend to look to their right when retelling a positive memory.

I have collected 28 responses over the week tracking different expressions of body language for varying ages and genders. I want to know if a certain gender or age group will lean towards a certain Positive Gestural Hemispheric Tendency.

```{r}

#==========================================================================
library(tidyverse)
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTo6sW3JxZZDW4p_VaIO5nu8c6ewzvMjWxlAKhhlZ0G9pgl4nCMspSJze20D3_BW6xDbM5At4L12ys1/pub?output=csv")
#==========================================================================


#Initialising data=========================================================
latest_data <- rename(logged_data, GenderOfPerson = Gender, Age = Age..estimation., PGHT = Positive.Gestural.Hemispheric.Tendency)

mean_age <- mean(latest_data$Age, na.rm = TRUE)
max_pght <- max(latest_data$PGHT, na.rm = TRUE)
n_males <- length(latest_data$GenderOfPerson[latest_data$GenderOfPerson == "Male"])
n_females <- length(latest_data$GenderOfPerson[latest_data$GenderOfPerson == "Female"])

n_left <- length(latest_data$PGHT[latest_data$PGHT == "Left"])
n_right <- length(latest_data$PGHT[latest_data$PGHT == "Right"])
#==========================================================================


#Calling summary dat=======================================================

cat(paste("The average age in the dataset is", round(mean_age, 1), "years."))
cat("\n")
cat(paste("There are", n_left, "individuals with a 'Left' PGHT compared to the", n_right, "individuals with a 'right' PGHT, indicating a notable tendency in gestural behavior towards the right"))

#==========================================================================



#Bar Graphs=================================================================

ggplot(latest_data, aes(x = PGHT, fill = GenderOfPerson)) + 
  geom_bar(position = "dodge") +
  labs(title = "PGHT Tendency by Gender", 
       subtitle = "Side-by-side comparison", 
       x = "Positive Gestural Hemispheric Tendency", 
       y = "Count", 
       caption = "Data from logged_data")

ggplot(latest_data, aes(x = Age, fill = PGHT)) + 
  geom_bar(position = "stack") +
  labs(title = "PGHT Distribution by Age", 
       subtitle = "Stacked tendencies across age groups", 
       x = "Age", 
       y = "Count", 
       caption = "Source: logged_data")
#==========================================================================

```
